A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 5_generalization.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

\paragraph{Outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Constant bead count}
We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.

>>>>

\paragraph{Outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Constant bead count}
We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
Additionally in order to emulate their definition of branches we mark all ST edges and in a separate algorithm we unmark the outer edges connected to the outline shape.
Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.

### 2019-08-23 8_discussion.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
See \cref{naive_overfill_underfill}
Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the graph of the ST.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
The toolpaths generated using our framework therefore remain the same when extra bones are added to the ST.

@@

The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.

>>>>

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
See \cref{naive_overfill_underfill}
Note also that contrary to some literature we don't remove edges from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there wasn't any edge in that region.
The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.

@@

The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.
